Setup for Neuroimaging on JHPCE Cluster
==========

First off, you should highly consider a Unix-like system.  [Cygwin](https://www.cygwin.com/) alongside [PuTTY](http://www.chiark.greenend.org.uk/~sgtatham/putty/) may work well, but I haven't tested it, don't have answers, and don't want to be the person you come to for questions.

Let's begin by locating your `.bash_profile`, which should be located at `~/.bash_profile`.  You can edit using `vi`.  

If you use `vi`, to insert something just type `i` and then copy and paste the code and then to write the file and quit, type `ESC+:+wq`.  The `ESC` escapes anything you were doing (like inserting text), the `w` means write the file, and `q` means quit.  If you edited a file and don't want to save changes, use `:q!`.  

I don't use `vi` and recommend [`Sublime Text`](http://www.sublimetext.com/), and setting it up to [edit files locally](http://www.danieldemmel.me/blog/2012/09/02/setting-up-rmate-with-sublime-text-for-remote-file-editing-over-ssh/), and another link [here](http://pogidude.com/2013/how-to-edit-a-remote-file-over-ssh-using-sublime-text-and-rmate/).  Make an [alias]() in your `~/.bash_profile` by adding the content:
```{r, engine='bash'}
alias subl="rmate -p MYPORTHERE"
```
where `MYPORTHERE` is a number that you set (that hopefully doesn't conflict with others).  Then you can do `subl filename.ext` while you are on JHPCE (**not a node**) and the file will open on your local machine.

## FSL Installation

We will first add [FSL](http://fsl.fmrib.ox.ac.uk/fsl/fslwiki/) to your `~/.bash_profile`, so you can use functions.

```{r, engine='bash', eval=FALSE}
# FSL Configuration
FSLDIR=/dexter/disk2/smart/programs/local/fsl
PATH=${FSLDIR}/bin:${PATH}
source ${FSLDIR}/etc/fslconf/fsl.sh
. ${FSLDIR}/etc/fslconf/fsl.sh
export FSLDIR PATH
```

## ANTsR

You can install [Install ANTsR from GitHuB](http://stnava.github.io/ANTsR/), which I recommend.  But if you want to get started with ANTsR right now (and download the gitHub later), you can use the following command in `R`:

```{r, eval=FALSE}
.libPaths( c( .libPaths(), "/dexter/disk2/smart/programs/R_Packages") )
```